SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-06-28 scipy-1.0/paper.tex
Added my name to authors list
DOC: Add affiliation
Correctly capitalize SymPy.

\author[1]{Pauli Virtanen}
\author[2,*]{Ralf Gommers}
\author[3,4]{Tyler Reddy}
\author[5]{Anne Archibald}
\author[6]{Andrew R. J. Nelson}
\author[7]{Charles Harris}
\author[8]{CJ Carey}
\author[9]{Denis Laxalde}
\author[10]{Eric Larson}
\author[11]{Eric Moore}
\author[12]{Eric Quintero}
\author[13]{Evgeni Burovski}
\author[14]{Jaime Fernández del Río}
\author[15]{Josef Perktold}
\author[16]{Josh Wilson}
\author[17]{Matthew Brett}
\author[18]{Nikolay Mayorov}
\author[19]{Warren Weckesser}
\author[20]{Matt Haberland}
\author[21]{Scott Sievert}
\author[22]{Yu Feng}
\author[23]{Antonio Horta Ribeiro}
\author[24]{Ian Henriksen}
\author[3,25]{K. Jarrod Millman}
\author[3]{St\'efan J. van der Walt}

\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[3]{Berkeley Institute for Data Science, University of California, Berkeley, CA, 94720, USA}
\affil[4]{Los Alamos National Laboratory,
	  Theoretical Division 6,
          Los Alamos, NM, 87545, USA}
\affil[5]{Affiliation, department, city, postcode, country}
\affil[6]{Australian Nuclear Science and Technology Organisation, Locked Bag 2001, Kirrawee DC, NSW 2232, Australia}
\affil[7]{Affiliation, department, city, postcode, country}
\affil[8]{Affiliation, department, city, postcode, country}
\affil[9]{Affiliation, department, city, postcode, country}
\affil[10]{Affiliation, department, city, postcode, country}
\affil[11]{Affiliation, department, city, postcode, country}
\affil[12]{Affiliation, department, city, postcode, country}
\affil[13]{Affiliation, department, city, postcode, country}
\affil[14]{Affiliation, department, city, postcode, country}
\affil[15]{Affiliation, department, city, postcode, country}
\affil[16]{Affiliation, department, city, postcode, country}
\affil[17]{Affiliation, department, city, postcode, country}
\affil[18]{Affiliation, department, city, postcode, country}
\affil[19]{Affiliation, department, city, postcode, country}
\affil[20]{BioResource and Agricultural Engineering, California Polytechnic State University, San Luis Obispo, CA, 93407, USA}
\affil[21]{Affiliation, department, city, postcode, country}
\affil[22]{Affiliation, department, city, postcode, country}
\affil[23]{Affiliation, department, city, postcode, country}
\affil[24]{University of Texas at Austin,
           Oden Institute for Computational Engineering and Sciences,
	   Austin, TX, 78712, USA}
\affil[25]{Division of Biostatistics, University of California,
  Berkeley, CA, 94720, USA}

@@

SciPy provides fundamental algorithms for scientific computing. The
breadth of its scope was derived from the Guide to Available Mathematical
Software classification system (GAMS\cite{boisvert1991guide}). In areas
that move relatively slowly, e.g. linear algebra, SciPy aims to provide
complete coverage. In other areas it aims to provide fundamental building
blocks while interacting well with other packages specialized in that area.
For example, SciPy provides what one expects to find in a
statistics textbook (probability distributions, hypothesis tests, frequency
statistics, correlation functions, and more), while 
Statsmodels\cite{statsmodels2010} provides
more advanced statistical estimators and inference methods;
scikit-learn\cite{pedregosa2011scikit} covers machine learning; and
PyMC3\cite{10.7717/peerj-cs.55}, emcee\cite{2013PASP-emcee} and 
PyStan\cite{pystan-ref} cover Bayesian statistics and probabilistic modeling.
scikit-image\cite{vanderwalt2014scikit} provides image processing
capabilities beyond SciPy's \texttt{ndimage}, sympy\cite{meurer2017sympy}
provides a Python interface for symbolic computation, and
while \texttt{sparse.csgraph} or \texttt{spatial} offers basic tools
for working with graphs and networks compared to a more specialized
Python library like NetworkX\cite{hagberg2008networkx}.

>>>>

\author[1]{Pauli Virtanen}
\author[2,*]{Ralf Gommers}
\author[3,4]{Tyler Reddy}
\author[5]{Anne Archibald}
\author[6]{Andrew R. J. Nelson}
\author[7]{Charles Harris}
\author[8]{CJ Carey}
\author[9]{Denis Laxalde}
\author[10]{Eric Larson}
\author[11]{Eric Moore}
\author[12]{Eric Quintero}
\author[13]{Evgeni Burovski}
\author[14]{Jaime Fernández del Río}
\author[15]{Josef Perktold}
\author[16]{Josh Wilson}
\author[17]{Matthew Brett}
\author[18]{Nikolay Mayorov}
\author[19]{Warren Weckesser}
\author[20]{Matt Haberland}
\author[21]{Scott Sievert}
\author[22]{Yu Feng}
\author[23]{Antonio Horta Ribeiro}
\author[24]{Ian Henriksen}
\author[3,25]{K. Jarrod Millman}
\author[3]{St\'efan J. van der Walt}
\author[26]{\.{I}lhan Polat}

\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[3]{Berkeley Institute for Data Science, University of California, Berkeley, CA, 94720, USA}
\affil[4]{Los Alamos National Laboratory,
	  Theoretical Division 6,
          Los Alamos, NM, 87545, USA}
\affil[5]{Affiliation, department, city, postcode, country}
\affil[6]{Australian Nuclear Science and Technology Organisation, Locked Bag 2001, Kirrawee DC, NSW 2232, Australia}
\affil[7]{Affiliation, department, city, postcode, country}
\affil[8]{Affiliation, department, city, postcode, country}
\affil[9]{Affiliation, department, city, postcode, country}
\affil[10]{University of Washington, Institute for Learning and Brain Sciences, Seattle, WA, 98195, USA}
\affil[11]{Affiliation, department, city, postcode, country}
\affil[12]{Affiliation, department, city, postcode, country}
\affil[13]{Affiliation, department, city, postcode, country}
\affil[14]{Affiliation, department, city, postcode, country}
\affil[15]{Affiliation, department, city, postcode, country}
\affil[16]{Affiliation, department, city, postcode, country}
\affil[17]{Affiliation, department, city, postcode, country}
\affil[18]{Affiliation, department, city, postcode, country}
\affil[19]{Affiliation, department, city, postcode, country}
\affil[20]{BioResource and Agricultural Engineering, California Polytechnic State University, San Luis Obispo, CA, 93407, USA}
\affil[21]{Affiliation, department, city, postcode, country}
\affil[22]{Affiliation, department, city, postcode, country}
\affil[23]{Affiliation, department, city, postcode, country}
\affil[24]{University of Texas at Austin,
           Oden Institute for Computational Engineering and Sciences,
	   Austin, TX, 78712, USA}
\affil[25]{Division of Biostatistics, University of California,
  Berkeley, CA, 94720, USA}
\affil[26]{Affiliation, department, city, postcode, country}

@@

SciPy provides fundamental algorithms for scientific computing. The
breadth of its scope was derived from the Guide to Available Mathematical
Software classification system (GAMS\cite{boisvert1991guide}). In areas
that move relatively slowly, e.g. linear algebra, SciPy aims to provide
complete coverage. In other areas it aims to provide fundamental building
blocks while interacting well with other packages specialized in that area.
For example, SciPy provides what one expects to find in a
statistics textbook (probability distributions, hypothesis tests, frequency
statistics, correlation functions, and more), while 
Statsmodels\cite{statsmodels2010} provides
more advanced statistical estimators and inference methods;
scikit-learn\cite{pedregosa2011scikit} covers machine learning; and
PyMC3\cite{10.7717/peerj-cs.55}, emcee\cite{2013PASP-emcee} and 
PyStan\cite{pystan-ref} cover Bayesian statistics and probabilistic modeling.
scikit-image\cite{vanderwalt2014scikit} provides image processing
capabilities beyond SciPy's \texttt{ndimage}, SymPy\cite{meurer2017sympy}
provides a Python interface for symbolic computation, and
while \texttt{sparse.csgraph} or \texttt{spatial} offers basic tools
for working with graphs and networks compared to a more specialized
Python library like NetworkX\cite{hagberg2008networkx}.
